---
title: "Continuous Shiny Test"
output: html_document
resource_files:
- shinycannon.sh
- recording.log
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shinyloadtest)
library(fs)
library(vroom)
library(purrr)
library(blastula)
library(lubridate)
app_url <- "https://colorado.rstudio.com/rsc/helloshiny"
```

This is a demo of how to use R Markdown to proactively test for shiny application failures. It can be very annoying if a user discovers that a shiny application is broken! To prevent this scenario, you can proactively test your shiny app on a regular interval by publishing and scheduling this RMD.

If the app test is successful, this RMD reports some simple timing information to create a record of how your app is responding.

If the app test fails, this RMD sends you an email alerting you to the problem.

Application tests can be as simple or as involved as you want, taking full advantage of the shinyloadtest framework for recording and replaying tests.

App to test: https://colorado.rstudio.com/rsc/helloshiny


## Step 1: Create a test

This is only done once and is not included in our regular scheduled rendering.

```{r eval=FALSE}
shinyloadtest::record_session(
  target_app_url = app_url,
  open_browser = FALSE
)
```

## Step 2 - Run the test

This step has a couple of pre-reqs:

1. You must have Java downloaded and installed on the path

2. You must have the shinycannon.sh file be executable. You can wget it from here: https://rstudio.github.io/shinyloadtest/articles/shinycannon.html (use the mac link, not the deb)

Be sure to update the command to use the correct URL, and to include connect auth if necessary!


```{bash results='hide'}
chmod +x ./shinycannon.sh
./shinycannon.sh ./recording.log 'https://colorado.rstudio.com/rsc/helloshiny' --overwrite-output --loaded-duration-minutes 1 --output-dir test --log-level info
```

## Step 3 - Determine results

The prior step generates some logs in a test directory which we can use to display success criteria or alert on failure.



```{r message=FALSE}
# check playback sessions for failures
Sys.setenv("VROOM_SHOW_PROGRESS"="false")

files <- fs::dir_ls("test/sessions")
check_failure <- function(rel_filepath) {
  res <- vroom::vroom(rel_filepath, delim = ",",skip = 2 )
  "PLAYBACK_FAIL" %in% res$event
}
test_results <- map_lgl(files, check_failure)

if(sum(test_results) > 0 ){
  failed <- TRUE
  sprintf("Unfortunately %d tests failed", sum(test_results))
} else {
  failed <- FALSE
  sprintf("All tests were successful!")
}
```

## Step 4 - Do some conditional alerting

```{r}
if (!failed) {
  timing_results <- load_runs("test")
  p1 <- slt_hist_loadtimes(timing_results)
  p2 <- slt_http_latency(timing_results)
  p3 <- slt_websocket_latency(timing_results)
  blastula::suppress_scheduled_email()
  list(p1,p2,p3)
} else {
  blastula::render_connect_email(
    "alert-email.Rmd"
  ) %>% 
  blastula::attach_connect_email(
    subject = sprintf("App Content Failure: %s ", app_url)
  )
}
```
